cardinalR: Generating interesting high-dimensional data structures

### 2025-09-20 paper-cardinalR.Rmd
Updated branching section

```{r}
cube_tb <- tibble(fun = c("gen_gridcube",
                          "gen_unifcube",
                          "gen_cubehole"), 
                      exp = c("Generate a cube with specified grid points along each axes.",
                              "Generate a cube with uniform points.", 
                              "Generate a cube with a hole."))
```

@@

```{r}
polynomial_tb <- tibble(fun = c("gen_quadratic",
                                "gen_cubic"), 
                        exp = c("Generate a quadratic pattern.",
                                "Generate a cubic pattern."))
```

@@

```{r}
scurve_tb <- tibble(fun = c("gen_scurve",
                            "gen_scurvehole"), 
                        exp = c("Generate a S-curve.",
                                "Generate a S-curve with a hole."))
```

@@

```{r}
sphere_tb <- tibble(fun = c("gen_circle",
                            "gen_curvycycle",
                            "gen_unifsphere",
                            "gen_gridedsphere",
                            "gen_clusteredspheres",
                            "gen_hemisphere"), 
                        exp = c("Generate a circle.",
                                "Generate a curvy cell cycle.",
                                "Generate a uniform sphere.",
                                "Generate a grided sphere.",
                                "Generate multiple small spheres within a big sphere.",
                                "Generate a hemisphere."))
```

@@

```{r}
trigonometric_tb <- tibble(fun = c("gen_crescent",
                            "gen_curvycylinder",
                            "gen_sphericalspiral",
                            "gen_helicalspiral",
                            "gen_conicspiral",
                            "gen_nonlinear"), 
                        exp = c("Generate a crescent pattern.",
                                "Generate a curvy cylinder.",
                                "Generate a spherical spiral.",
                                "Generate a helical spiral.",
                                "Generate a conic spiral.",
                                "Generate a nonlinear hyperbola."))
```

@@

```{r}
trefoil_tb <- tibble(fun = c("gen_trefoil4d",
                            "gen_trefoil3d"), 
                        exp = c("Generate a trefoil in $4\\text{-}D$.",
                                "Generate a trefoil in $3\\text{-}D$."))
```

@@

```{r}
odd_shapes_tb <- tibble(fun = c("make_mobiusgau",
                                "make_multigau",
                                "make_curvygau",
                                "make_klink_circles",
                                "make_chain_circles",
                                "make_klink_curvycycle",
                                "make_chain_curvycycle",
                                "make_gaucircles",
                                "make_gaucurvycycle",
                                "make_onegrid",
                                "make_twogrid_overlap",
                                "make_twogrid_shift",
                                "make_shape_para",
                                "make_three_clust_"), 
                        exp = c(
    "Generates a Möbius-like cluster combined with a Gaussian cluster.",
    "Generates multiple Gaussian clusters in high-dimensional space.",
    "Generates a curvilinear cluster with a Gaussian cluster.",
    "Generates K-link circular clusters (non-linear circular patterns).",
    "Generates chain-like circular clusters connected sequentially.",
    "Generates K-link curvy cycle clusters (curvilinear loop structures).",
    "Generates chain-like curvy cycle clusters connected sequentially.",
    "Generates circular clusters with a Gaussian cluster in the middle.",
    "Generates curvy circular clusters with a Gaussian cluster in the middle.",
    "Generates a single grid in two dimensions.",
    "Generates two overlapping grids.",
    "Generates two grids shifted relative to each other.",
    "Generates parallel shaped clusters.",
    "Generates three clusters with different shapes. (eg:- 01, 02, ..., 20)"))
```

>>>>

```{r}
cube_tb <- tibble(fun = c("gen_gridcube",
                          "gen_unifcube",
                          "gen_cubehole"), 
                      exp = c("Cube with specified grid points along each axes.",
                              "Cube with uniform points.", 
                              "Cube with a hole."))
```

@@

```{r}
polynomial_tb <- tibble(fun = c("gen_quadratic",
                                "gen_cubic"), 
                        exp = c("Quadratic pattern.",
                                "Cubic pattern."))
```

@@

```{r}
scurve_tb <- tibble(fun = c("gen_scurve",
                            "gen_scurvehole"), 
                        exp = c("S-curve.",
                                "S-curve with a hole."))
```

@@

```{r}
sphere_tb <- tibble(fun = c("gen_circle",
                            "gen_curvycycle",
                            "gen_unifsphere",
                            "gen_gridedsphere",
                            "gen_clusteredspheres",
                            "gen_hemisphere"), 
                        exp = c("Circle.",
                                "Curvy cell cycle.",
                                "Uniform sphere.",
                                "Grided sphere.",
                                "Multiple small spheres within a big sphere.",
                                "Hemisphere."))
```

@@

```{r}
trigonometric_tb <- tibble(fun = c("gen_crescent",
                            "gen_curvycylinder",
                            "gen_sphericalspiral",
                            "gen_helicalspiral",
                            "gen_conicspiral",
                            "gen_nonlinear"), 
                        exp = c("Crescent pattern.",
                                "Curvy cylinder.",
                                "Spherical spiral.",
                                "Helical spiral.",
                                "Conic spiral.",
                                "Nonlinear hyperbola."))
```

@@

```{r}
trefoil_tb <- tibble(fun = c("gen_trefoil4d",
                            "gen_trefoil3d"), 
                        exp = c("Trefoil in $4\\text{-}D$.",
                                "Trefoil in $3\\text{-}D$."))
```

@@

```{r}
odd_shapes_tb <- tibble(fun = c("make_mobiusgau",
                                "make_multigau",
                                "make_curvygau",
                                "make_klink_circles",
                                "make_chain_circles",
                                "make_klink_curvycycle",
                                "make_chain_curvycycle",
                                "make_gaucircles",
                                "make_gaucurvycycle",
                                "make_onegrid",
                                "make_twogrid_overlap",
                                "make_twogrid_shift",
                                "make_shape_para",
                                "make_three_clust_"), 
                        exp = c(
    "Möbius-like cluster combined with a Gaussian cluster.",
    "Multiple Gaussian clusters in high-dimensional space.",
    "Curvilinear cluster with a Gaussian cluster.",
    "K-link circular clusters (non-linear circular patterns).",
    "Chain-like circular clusters connected sequentially.",
    "K-link curvy cycle clusters (curvilinear loop structures).",
    "Chain-like curvy cycle clusters connected sequentially.",
    "Circular clusters with a Gaussian cluster in the middle.",
    "Curvy circular clusters with a Gaussian cluster in the middle.",
    "Single grid in two dimensions.",
    "Two overlapping grids.",
    "Two grids shifted relative to each other.",
    "Parallel shaped clusters.",
    "Three clusters with different shapes. (eg:- 01, 02, ..., 20)"))
```

### 2025-09-20 paper-cardinalR.tex
Updated branching section

\caption{\label{tab:cube-tb-pdf}cardinalR cube data generation functions}
\centering
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{4cm}>{\raggedright\arraybackslash}p{8cm}}
\toprule
Function & Explanation\\
\midrule
gen\_gridcube & Generate a cube with specified grid points along each axes.\\
gen\_unifcube & Generate a cube with uniform points.\\
gen\_cubehole & Generate a cube with a hole.\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:polynomial-tb-pdf}cardinalR polynomial data generation functions}
\centering
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{4cm}>{\raggedright\arraybackslash}p{8cm}}
\toprule
Function & Explanation\\
\midrule
gen\_quadratic & Generate a quadratic pattern.\\
gen\_cubic & Generate a cubic pattern.\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:scurve-tb-pdf}cardinalR S-curve data generation functions}
\centering
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{4cm}>{\raggedright\arraybackslash}p{8cm}}
\toprule
Function & Explanation\\
\midrule
gen\_scurve & Generate a S-curve.\\
gen\_scurvehole & Generate a S-curve with a hole.\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:sphere-tb-pdf}cardinalR sphere data generation functions}
\centering
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{4cm}>{\raggedright\arraybackslash}p{8cm}}
\toprule
Function & Explanation\\
\midrule
gen\_circle & Generate a circle.\\
gen\_curvycycle & Generate a curvy cell cycle.\\
gen\_unifsphere & Generate a uniform sphere.\\
gen\_gridedsphere & Generate a grided sphere.\\
gen\_clusteredspheres & Generate multiple small spheres within a big sphere.\\
\addlinespace
gen\_hemisphere & Generate a hemisphere.\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:trigonometric-tb-pdf}cardinalR trigonometric data generation functions}
\centering
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{4cm}>{\raggedright\arraybackslash}p{8cm}}
\toprule
Function & Explanation\\
\midrule
gen\_crescent & Generate a crescent pattern.\\
gen\_curvycylinder & Generate a curvy cylinder.\\
gen\_sphericalspiral & Generate a spherical spiral.\\
gen\_helicalspiral & Generate a helical spiral.\\
gen\_conicspiral & Generate a conic spiral.\\
\addlinespace
gen\_nonlinear & Generate a nonlinear hyperbola.\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:trefoil-tb-pdf}cardinalR trefoil data generation functions}
\centering
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{4cm}>{\raggedright\arraybackslash}p{8cm}}
\toprule
Function & Explanation\\
\midrule
gen\_trefoil4d & Generate a trefoil in \$4\textbackslash{}text\{-\}D\$.\\
gen\_trefoil3d & Generate a trefoil in \$3\textbackslash{}text\{-\}D\$.\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:odd-shape-tb-pdf}cardinalR multiple clusters generation functions}
\centering
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{4cm}>{\raggedright\arraybackslash}p{8cm}}
\toprule
Function & Explanation\\
\midrule
make\_mobiusgau & Generates a Möbius-like cluster combined with a Gaussian cluster.\\
make\_multigau & Generates multiple Gaussian clusters in high-dimensional space.\\
make\_curvygau & Generates a curvilinear cluster with a Gaussian cluster.\\
make\_klink\_circles & Generates K-link circular clusters (non-linear circular patterns).\\
make\_chain\_circles & Generates chain-like circular clusters connected sequentially.\\
\addlinespace
make\_klink\_curvycycle & Generates K-link curvy cycle clusters (curvilinear loop structures).\\
make\_chain\_curvycycle & Generates chain-like curvy cycle clusters connected sequentially.\\
make\_gaucircles & Generates circular clusters with a Gaussian cluster in the middle.\\
make\_gaucurvycycle & Generates curvy circular clusters with a Gaussian cluster in the middle.\\
make\_onegrid & Generates a single grid in two dimensions.\\
\addlinespace
make\_twogrid\_overlap & Generates two overlapping grids.\\
make\_twogrid\_shift & Generates two grids shifted relative to each other.\\
make\_shape\_para & Generates parallel shaped clusters.\\
make\_three\_clust\_ & Generates three clusters with different shapes. (eg:- 01, 02, ..., 20)\\
\bottomrule
\end{tabular}
\end{table}

>>>>

\caption{\label{tab:cube-tb-pdf}cardinalR cube data generation functions}
\centering
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{4cm}>{\raggedright\arraybackslash}p{8cm}}
\toprule
Function & Explanation\\
\midrule
gen\_gridcube & Cube with specified grid points along each axes.\\
gen\_unifcube & Cube with uniform points.\\
gen\_cubehole & Cube with a hole.\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:polynomial-tb-pdf}cardinalR polynomial data generation functions}
\centering
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{4cm}>{\raggedright\arraybackslash}p{8cm}}
\toprule
Function & Explanation\\
\midrule
gen\_quadratic & Quadratic pattern.\\
gen\_cubic & Cubic pattern.\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:scurve-tb-pdf}cardinalR S-curve data generation functions}
\centering
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{4cm}>{\raggedright\arraybackslash}p{8cm}}
\toprule
Function & Explanation\\
\midrule
gen\_scurve & S-curve.\\
gen\_scurvehole & S-curve with a hole.\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:sphere-tb-pdf}cardinalR sphere data generation functions}
\centering
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{4cm}>{\raggedright\arraybackslash}p{8cm}}
\toprule
Function & Explanation\\
\midrule
gen\_circle & Circle.\\
gen\_curvycycle & Curvy cell cycle.\\
gen\_unifsphere & Uniform sphere.\\
gen\_gridedsphere & Grided sphere.\\
gen\_clusteredspheres & Multiple small spheres within a big sphere.\\
\addlinespace
gen\_hemisphere & Hemisphere.\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:trigonometric-tb-pdf}cardinalR trigonometric data generation functions}
\centering
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{4cm}>{\raggedright\arraybackslash}p{8cm}}
\toprule
Function & Explanation\\
\midrule
gen\_crescent & Crescent pattern.\\
gen\_curvycylinder & Curvy cylinder.\\
gen\_sphericalspiral & Spherical spiral.\\
gen\_helicalspiral & Helical spiral.\\
gen\_conicspiral & Conic spiral.\\
\addlinespace
gen\_nonlinear & Nonlinear hyperbola.\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:trefoil-tb-pdf}cardinalR trefoil data generation functions}
\centering
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{4cm}>{\raggedright\arraybackslash}p{8cm}}
\toprule
Function & Explanation\\
\midrule
gen\_trefoil4d & Trefoil in \$4\textbackslash{}text\{-\}D\$.\\
gen\_trefoil3d & Trefoil in \$3\textbackslash{}text\{-\}D\$.\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:odd-shape-tb-pdf}cardinalR multiple clusters generation functions}
\centering
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{4cm}>{\raggedright\arraybackslash}p{8cm}}
\toprule
Function & Explanation\\
\midrule
make\_mobiusgau & Möbius-like cluster combined with a Gaussian cluster.\\
make\_multigau & Multiple Gaussian clusters in high-dimensional space.\\
make\_curvygau & Curvilinear cluster with a Gaussian cluster.\\
make\_klink\_circles & K-link circular clusters (non-linear circular patterns).\\
make\_chain\_circles & Chain-like circular clusters connected sequentially.\\
\addlinespace
make\_klink\_curvycycle & K-link curvy cycle clusters (curvilinear loop structures).\\
make\_chain\_curvycycle & Chain-like curvy cycle clusters connected sequentially.\\
make\_gaucircles & Circular clusters with a Gaussian cluster in the middle.\\
make\_gaucurvycycle & Curvy circular clusters with a Gaussian cluster in the middle.\\
make\_onegrid & Single grid in two dimensions.\\
\addlinespace
make\_twogrid\_overlap & Two overlapping grids.\\
make\_twogrid\_shift & Two grids shifted relative to each other.\\
make\_shape\_para & Parallel shaped clusters.\\
make\_three\_clust\_ & Three clusters with different shapes. (eg:- 01, 02, ..., 20)\\
\bottomrule
\end{tabular}
\end{table}
